\documentclass{article}
\usepackage{amsmath, amssymb, amsthm}

\setlength{\parindent}{0pt}

\newtheorem*{claim}{Claim}

\begin{document}

\begin{claim}
    Let $G$ be a connected graph. $G$ has an Eulerian circuit if and only if every vertex of $G$ has even degree.
\end{claim}

\begin{proof}
    Assume $G$ has an Eulerian circuit $C$.

    \medskip

    Consider any arbitrary vertex $v$. Every time the circuit arrives at $v$, it must also leave $v$ along a 
    different edge. Thus the edges incident to $v$ can be paired up as one edge used to enter $v$ and one edge used 
    to leave $v$. Therefore the incident edges occur in pairs, meaning $\deg(v)$ is even. Since $v$ is arbitrary, 
    every vertex of $G$ has even degree.

    \medskip

    Assume every vertex of $G$ has even degree. We then induct on the number of edges in $G$.

    \medskip

    \textbf{Base case:} If $G$ has no edges, i.e. one vertex, the statement is trivially true.

    \medskip

    \textbf{Inductive step:} We assume that every connected graph with $n$ edges and even degree vertices has an 
    Eulerian circuit. Let $H$ be a connected graph with $n+1$ edges and even degree vertices. Since every vertex 
    has even degree, every vertex has degree at least $2$. Hence any maximal path in $H$ must eventually revisit a 
    vertex, forming a cycle $C$.

    \medskip
    
    Remove the edges of $C$ from $H$, leaving a graph $H'$. Let $H_1,\dots,H_k$ be the connected components of $H'$. 
    Each $H_i$ is connected by definition, and has all even degrees since removing the edges of $C$ reduces the 
    degree of cycle vertices by exactly $2$. By the inductive hypothesis, each $H_i$ has an Eulerian circuit. Since 
    $H$ was connected, each $H_i$ shares at least one vertex with $C$. By splicing the Eulerian circuit of each $H_i$
    into $C$, we obtain an Eulerian circuit for $H$. Therefore $H$ has an Eulerian circuit.

    \medskip

    Hence $G$ has an Eulerian circuit if and only if every vertex of $G$ has even degree.
\end{proof}

\end{document}
