\documentclass{article}
\usepackage{amsmath, amssymb, amsthm}

\setlength{\parindent}{0pt}

\newtheorem{claim}{Claim}

\begin{document}

\begin{claim}
    You can tile an $8 \times 8$ chessboard with $32$ dominoes.
\end{claim}

\begin{proof}
    Partition the board into rows. Each row consists of $8$ squares,
    which can be tiled with $4$ horizontal dominoes placed end-to-end.
    Applying this to all $8$ rows yields a valid tiling using 
    $8 \times 4 = 32$ dominoes, covering all $8 \times 8 = 64$ squares
    with no overlap.
\end{proof}

\begin{claim}
    You cannot tile an $8 \times 8$ chessboard with $31$ dominoes
    if the opposite corners are removed.
\end{claim}

\begin{proof}
    On a standard $8 \times 8$ chessboard, there are $32$ black and $32$ white 
    squares. Since opposite corners have row and column indices of the same 
    parity, they must have the same colour. Without loss of generality, assume 
    both are white. Removing them leaves $32$ black and $30$ white squares.

    \medskip
    
    Every domino covers exactly one black square and one white square,
    so any tiling by $31$ dominoes covers exactly $31$ black and $31$ white squares. 
    This contradicts the board having $32$ black and $30$ white squares. 
    Therefore no such tiling exists.
\end{proof}

\begin{claim}
    Given a truncated chessboard, there exists a bipartite graph $G$
    that has a perfect matching if and only if the chessboard can be
    tiled with dominoes.
\end{claim}

\begin{proof}
    Colour the truncated chessboard like a standard chessboard. Let $B$
    and $W$ be the sets of remaining black and white squares respectively.
    Construct a bipartite graph $G = (B \cup W, E)$ where two squares
    $b \in B$ and $w \in W$ are joined by an edge if and only if they
    are adjacent on the board.

    \medskip
    
    Suppose first that $G$ has a perfect matching $M$.
    Since every edge in $M$ joins two adjacent squares, we can place a
    domino on each such pair of squares. Because $M$ is perfect, every
    square is incident to exactly one edge of $M$, so every square is
    covered by exactly one domino. Hence the chessboard is tiled by
    dominoes.

    \medskip
    
    Conversely, suppose that the chessboard is tiled by dominoes.
    Each domino covers exactly two adjacent squares, one black and one white,
    so each domino determines an edge of $G$. Since the dominoes are disjoint
    and cover every square exactly once, the corresponding edges form a perfect
    matching of $G$.

    \medskip
    
    Therefore the chessboard can be tiled by dominoes if and only if
    $G$ has a perfect matching.
\end{proof}

\begin{claim}
    A truncated chessboard can be tiled with dominoes if and only if for every
    set $S$ of black squares, there are at least $|S|$ white squares neighbouring
    $S$, and vice versa.
\end{claim}

\begin{proof}
    Let $G$ be the bipartite graph constructed in Claim 3. By Claim 3, the board is
    tilable with dominoes if and only if $G$ has a perfect matching.

    \medskip

    By Hall's theorem, $G$ has a perfect matching if and only if for every
    $S \subseteq B$, $|N(S)| \geq |S|$, and for every $S \subseteq W$,
    $|N(S)| \geq |S|$.

    \medskip

    Since edges in $G$ correspond to adjacent squares on the chessboard,
    $N(S)$ is precisely the set of white squares neighbouring $S$. Hence
    the condition $|N(S)| \geq |S|$ is equivalent to there being at least
    $|S|$ white squares neighbouring $S$, and vice versa. Therefore a
    truncated chessboard can be tiled with dominoes if and only if for
    every set $S$ of black squares, there are at least $|S|$ white squares
    neighbouring $S$, and vice versa.
\end{proof}

\end{document}
