\documentclass{article}
\usepackage{amsmath, amssymb, amsthm}

\setlength{\parindent}{0pt}

\newtheorem{claim}{Claim}

\begin{document}

\begin{claim}
    There are $20$ books arranged in a row on a shelf. There exists a bijection between choosing
    $6$ books so that no two adjacent books are selected and $15$-bit sequences with exactly $6$ 
    ones.
\end{claim}

\begin{proof}
    Let
    \[
    a_1 < a_2 < \dots < a_6
    \]
    be the positions of the $6$ chosen books where $a_{i+1} \ge a_i + 2$.

    \medskip

    Define
    \[
    b_i = a_i - (i - 1) \qquad i = 1, 2, \dots, 6
    \]
    This amounts to deleting one unselected book from each of the five gaps between consecutive 
    selected books, therefore shifting the $i$th selected book left by $i - 1$ positions. Since
    \[
    b_{i+1} - b_i = (a_{i+1} - a_i) - 1 \ge 1
    \]
    we have
    \[
    1 \le b_1 < b_2 < \dots < b_6 \le 20 - 5 = 15
    \]
    Thus $(b_1, \dots, b_6)$ determines a unique 15-bit sequence with ones in positions $b_1, \dots, 
    b_6$.

    \medskip

    Conversely, if $b_1 < b_2 < \dots < b_6$ are the positions of the ones in a 15-bit sequence, 
    define
    \[
    a_i = b_i + (i - 1)
    \]
    Then
    \[
    a_{i+1} - a_i = (b_{i+1} - b_i) + 1 \ge 2
    \]
    so the corresponding books are nonadjacent. Since the two constructions are inverses of each 
    other, they define a bijection.

    \medskip

    Hence there exists a bijection between choosing $6$ books so that no two adjacent books are 
    selected and $15$-bit sequences with exactly $6$ ones.
\end{proof}

\begin{claim}
    There are $5005$ ways to select $6$ books such that no two adjacent books 
    are selected. 
\end{claim}

\begin{proof}
    By Claim 1, there is a bijection between selections of $6$ books with no two adjacent and 
    $15$-bit sequences with exactly $6$ ones. Therefore it suffices to count the latter. Since 
    such a sequence is uniquely determined by the positions of its ones, the number of those 
    sequences is
    \[
    \binom{15}{6} = 5005
    \]

    \medskip

    Hence there are $5005$ ways to select $6$ books such that no two adjacent books are selected.
\end{proof}

\end{document}
